Time Series Bootstrapping For Solar Current

### 2021-12-16 deliverables/paper.Rmd
Fixed formatting and grammar

```{r knitr-opts, echo=FALSE}
knitr::opts_chunk$set(fig.pos = "t", fig.align = 'center', out.width = "75%", out.extra = "")
```

@@

This project began with the search for a research paper
utilizing the process of Monte Carlo sampling or other 
statistcal computing methods. We landed on a few papers 
that did exatcly this, one titled, "SolarStat: Modeling 
Photovoltaic Sources through Stochastic Markov Processes". 
Instead of comparing our works of Monte Carlo simulations 
we were able to utilize a more recent topic discussed in class.
This of course was bootsrapping, a topic we didn't get too in
depth about; however, everything needed to know will be explained 
later on in the paper. Regarding our choice of articles, it was a
question of interest and importance. During the last decade the world
has seen a massive uptick in renewable energy pushes. With this 
new wave of renewables and the rather large misunderstanding of their
total power we decided it would be interesting to look into solar and 
what it was all about. The big question being asked regarding
solar power is whether or not it is worth heading the initial cost
of set up and general mantienance. Many websites inform users of 
just this, according to the Solar.com Learning Center, the average
solar panel net cost is \$2,700 per 1.5 kilowatt-hour system (@solar.com). 
The biggest upside to solar panels is being able to slice down your 
energy bill, and eventually have it pay for itself. In order to 
calculate a solar panels net output experts recommend looking at three things. 
1. Determine your locations peak sun hours (average US around 4 hours/day)
2. Determine your energy compensation (average \$0.03/kilowatt-hour (kWh))
3. Determine your solar panels net energy output
Once you have calculated these three numbers it is as easy as 
multiplying them together to receive your daily solar panel 
compensation (@energysage). As an example Energy Sage looked at 
California receiving 5 peak hours of sunlight a day with a single 
solar panel producing 290 watts/hour. Daily, this panel will produce 
around 1.5 kWh per day yielding the owner a rough compensation 
of \$16.42 a year.

@@

It should be noted that the hourly distribution
of values for GHI and simulated power did not have
exactly the same shape,
as evidenced by Figure \ref{fig:ghi-hour-boxplot}
and Figure \ref{power-hour-boxplot}.
Both figures have values that,
on average, move upward throughout the day,
and then down towards zero at night.
Nighttime accounts for the structural zeros seen the figures.
The variation in the values over the day is due to expected
variation in radiation due to the seasons,
and random variation, like cloud cover.
Some of the random variation can be seen in
Figure \ref{fig:ghi-ts} and Figure \ref{fig:power-ts}.
The range of distributions in Figure \ref{power-hour-boxplot}
was used to guide the data filtering described in the next section.

@@

```{r unfiltered-hist, fig.cap = "Distribution of power outputs before filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
unfiltered_power_hist <- ggplot() +
  geom_histogram(aes(x = df$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(unfiltered_power_hist)
```

```{r filtered-hist, fig.cap = "Distribution of power outputs after filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(filtered_power_hist)
```

@@

```{r vis, echo=FALSE, warning=FALSE}
vis_df <- rbind(boot_block_df, boot_iid_df)

@@

```{r bootstrap-ci, echo=FALSE}
bootstrap_ci_table <- rbind(
c("iid", paste("(", round(iid_ci[1],3),",", round(iid_ci[2],3), ")")),
c("Block", paste("(", round(block_ci[1],3),",", round(block_ci[2], 3), ")"))
)
colnames(bootstrap_ci_table) <- c("Bootstrap Method", "95% CI")
rownames(bootstrap_ci_table) <- c()
bootstrap_ci_table %>% kable(booktabs = TRUE,
caption="95% confidence intervals for the mean simulated power, as generated by each of the two bootstrapping methods.")
```

@@

@@

These estimates provide consumers with an answer to 
a very pressing question. As discussed in the introduction, one of the biggest 
problems about purchasing a solar panel is whether or not 
it will end up paying for itself. One of the three stipulations in 
order to calculate your average yearly return is a solar 
panels output. After using bootstrapping we were able to 
calculate a solar panel in Los Angeles' production 
output being `r round(power_out_est_year/1000)`. Now, all 
that is needed is the peak hours and total average cost/kWh. 
The former can be calculated by setting a lower floor on 
solar irradiance. Stated on Solar Reviews, 
"1 peak sun hour" is equal to, "1000 W/m² of sunlight 
per hour" (@energysage). In our calculations we used an hour window between 
8am to 4pm, a typical day range where the sun is overhead. A disclaimer,
some of the values at the beginning and end of the day may not hold 
exactly greater than our cutoff stated by Solar Reviews, however this range 
yielded the greatest results of solar irradiance and Wh, some being much larger
than 1000 W/m^2 and others being just under. Therefore, we are deciding to use 
this range as our peak hours. Taking this total of `r length(HOUR_WINDOW)` 
peak hours and our average cost per kilowatt-hour of \$0.03 from before 
we would find that on average a consumer in Los Angeles can 
anticipate earning \$`r round(round(power_out_est_year/1000,2)*.03*length(HOUR_WINDOW),2)` yearly on one solar panel grid. 
Knowing this, any resident located in or around the Los Angeles area should
feel confident in their decision of purchasing a solar panel grid.

>>>>

```{r knitr-opts, echo=FALSE}
knitr::opts_chunk$set(fig.pos = "t", fig.align = 'center', out.width = "75%", out.extra = "",
message=FALSE, warning=FALSE)
```

@@

This project began with the search for a research paper
utilizing the process of Monte Carlo sampling or other 
statistcal computing methods. We landed on a few papers 
that did exatcly this, one titled, "SolarStat: Modeling 
Photovoltaic Sources through Stochastic Markov Processes". 
Instead of comparing our works of Monte Carlo simulations 
we were able to utilize a more recent topic discussed in class.
This of course was bootsrapping, a topic we didn't get too in
depth about; however, everything needed to know will be explained 
later on in the paper. Regarding our choice of articles, it was a
question of interest and importance. During the last decade the world
has seen a massive uptick in renewable energy pushes. With this 
new wave of renewables and the rather large misunderstanding of their
total power we decided it would be interesting to look into solar and 
what it was all about. The big question being asked regarding
solar power is whether or not it is worth heading the initial cost
of set up and general mantienance. Many websites inform users of 
just this, according to the Solar.com Learning Center, the average
solar panel net cost is \$2,700 per 1.5 kilowatt-hour system (@solar.com). 
The biggest upside to solar panels is being able to slice down your 
energy bill, and eventually have it pay for itself. In order to 
calculate a solar panels net output experts recommend looking at three things:

1. Determine your locations peak sun hours (average US around 4 hours/day)
2. Determine your energy compensation (average \$0.03/kilowatt-hour (kWh))
3. Determine your solar panels net energy output

Once you have calculated these three numbers it is as easy as 
multiplying them together to receive your daily solar panel 
compensation (@energysage). As an example Energy Sage looked at 
California receiving 5 peak hours of sunlight a day with a single 
solar panel producing 290 watts/hour. Daily, this panel will produce 
around 1.5 kWh per day yielding the owner a rough compensation 
of \$16.42 a year.

@@

It should be noted that the hourly distribution
of values for GHI and simulated power did not have
exactly the same shape,
as evidenced by Figure \ref{fig:ghi-hour-boxplot}
and Figure \ref{fig:power-hour-boxplot}.
Both figures have values that,
on average, move upward throughout the day,
and then down towards zero at night.
Nighttime accounts for the structural zeros seen the figures.
The variation in the values over the day is due to expected
variation in radiation due to the seasons,
and random variation, like cloud cover.
Some of the random variation can be seen in
Figure \ref{fig:ghi-ts} and Figure \ref{fig:power-ts}.
The range of distributions in Figure \ref{fig:power-hour-boxplot}
was used to guide the data filtering described in the next section.

@@

```{r unfiltered-hist, fig.cap = "Distribution of power outputs before filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
unfiltered_power_hist <- ggplot() +
  geom_histogram(aes(x = df$power_out, y = ..density..), bins=50) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(unfiltered_power_hist)
```

```{r filtered-hist, fig.cap = "Distribution of power outputs after filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..), bins=50) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(filtered_power_hist)
```

@@

```{r vis, echo=FALSE, warning=FALSE, message=FALSE}
vis_df <- rbind(boot_block_df, boot_iid_df)

@@

```{r bootstrap-ci, echo=FALSE}
bootstrap_ci_table <- rbind(
c("iid", paste("(", round(iid_ci[1],3),",", round(iid_ci[2],3), ")")),
c("Block", paste("(", round(block_ci[1],3),",", round(block_ci[2], 3), ")"))
)
colnames(bootstrap_ci_table) <- c("Bootstrap Method", "95 Percent CI")
rownames(bootstrap_ci_table) <- c()
bootstrap_ci_table %>% kable(booktabs = TRUE,
caption="95% confidence intervals for the mean simulated power, as generated by each of the two bootstrapping methods.")
```

@@

\pagebreak

@@

These estimates provide consumers with an answer to 
a very pressing question. As discussed in the introduction, one of the biggest 
problems about purchasing a solar panel is whether or not 
it will end up paying for itself. One of the three stipulations in 
order to calculate your average yearly return is a solar 
panels output. After using bootstrapping we were able to 
calculate a solar panel in Los Angeles' production 
output being `r round(power_out_est_year/1000)`. Now, all 
that is needed is the peak hours and total average cost per kWh. 
The former can be calculated by setting a lower floor on 
solar irradiance. As stated on Solar Reviews, 
"1 peak sun hour" is equal to, "1000 W/m² of sunlight 
per hour" (@energysage). In our calculations we used an hour window between 
8am to 4pm, a typical day range where the sun is overhead. As a disclaimer,
some of the values at the beginning and end of the day may not hold 
exactly greater than our cutoff stated by Solar Reviews, however this range 
yielded the greatest results of solar irradiance and Wh, some being much larger
than 1000 W/m^2 and others being just under. Therefore, we decided to use 
this range as our peak hours. Taking this total of `r length(HOUR_WINDOW)` 
peak hours and our average cost per kilowatt-hour of \$0.03 from before 
we would find that on average a consumer in Los Angeles can 
anticipate earning \$`r round(round(power_out_est_year/1000,2)*.03*length(HOUR_WINDOW),2)` yearly on one solar panel grid. 
Knowing this, any resident located in or around the Los Angeles area should
feel confident in their decision of purchasing a solar panel grid.
